CannonRV: Measuring radial velocities with a data-driven spectral model

### 2017-03-01 paper/ms.tex
Add plot
Biggest delta_RV between the two methods

\subsection{\label{sec:level2}optimize Teff , log g and [Fe/H] simultaneously with a, b, c}

@@

\begin{equation}
l_m \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n}-V(l_m)\cdot \theta_j)^2} \over {e^2_{j,n}}} \right]
\end{equation}

@@

\begin{equation}
l_m, a, b, c \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n} - a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1})^2} \over {e^2_{j,n}}} \right]
\end{equation}

@@

 After that, we show the histogram of parameters a, b and c.

@@

# We also compare the results from the whole spectrum(The original method) and fitting simultaneously.

@@

>>>>

\subsection{\label{sec:level2} Optimize Teff , log g and [Fe/H] simultaneously with a, b, c}

@@

\begin{equation}
l_m \leftarrow argmin \left[ \sum_{j=1}^{j=J}{({y_{j,n}-V(l_m)\cdot \theta_j)^2} \over {e^2_{j,n}}} \right]
\end{equation}

@@

\begin{equation}
l_m, a, b, c \leftarrow argmin \left[ \sum_{j=1}^{j=J}{({y_{j,n} - a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1})^2} \over {e^2_{j,n}}} \right]
\end{equation}

@@

After that, we show the histogram of parameters a, b and c, which are from individual visits of the 654 stars in the former experiment.

@@

We also compare the results from the whole spectrum(The original method) and fitting simultaneously.

@@

Finally, we choose the sixteen visits with biggest $delta_RV$, which is defined as the difference between the RV shifts from the whole spectrum(The original method) and simultaneous fitting.

 \begin{center}
\includegraphics[width=170mm]{big_delta_rv_sim.png}

\centerline{Fig.18 The visits with biggest $delta_RV$ part 1}

 \begin{center}
\includegraphics[width=170mm]{big_delta_rv_sim2.png}

\centerline{Fig.19 The visits with biggest $delta_RV$ part 2}

 \begin{center}
\includegraphics[width=170mm]{big_delta_rv_sim3.png}

\centerline{Fig.20 The visits with biggest $delta_RV$ part 4}

 \begin{center}
\includegraphics[width=170mm]{big_delta_rv_sim4.png}

\centerline{Fig.21 The visits with biggest $delta_RV$ part 4}
